\vspec{} and Friends: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-07-29 src/tex/ms.tex
Give source of Gao2022 data

Before simulating an observation, \vspec{} asks \texttt{vspec-vsm} to pre-compute a population of flares based on a power-law frequency-energy relationship similar to the results of \TJ{what data?} \citep{gao2022}:
\begin{equation} \label{eq:flare_freq}
    \log{(f/{\rm [day]})} = \beta + \alpha~\log{(E/{\rm [erg]})}
\end{equation}
where $f$ is the frequency of flares with energies $\ge E$. We compute the number of expected flares over a time duration and determine the number to create $N$ by a random Poisson draw. We then generate $N$ flares with energies determined by the quantile function:
\begin{equation}
    E = E_{\text{min}} (1-X)^{1/\alpha}
\end{equation}
where $E_{\text{min}}$ is the minimum considered flare energy and $X$ is a random number on the interval $[0,1)$. We set the default values $\alpha=-0.829$, $\beta=26.87$ from \citet{gao2022}, but these can be adjusted by the user. Figure \ref{fig:flare_freq} shows our simulation results compared to their power-law values.

>>>>

Before simulating an observation, \vspec{} asks \texttt{vspec-vsm} to pre-compute a population of flares based on a power-law frequency-energy relationship based on Kepler and TESS lightcurves \citep{gao2022}:
\begin{equation} \label{eq:flare_freq}
    \log{(f/{\rm [day]})} = \beta + \alpha~\log{(E/{\rm [erg]})}
\end{equation}
where $f$ is the frequency of flares with energies $\ge E$. We compute the number of expected flares over a time duration and determine the number to create $N$ by a random Poisson draw. We then generate $N$ flares with energies determined by the quantile function:
\begin{equation}
    E = E_{\text{min}} (1-X)^{1/\alpha}
\end{equation}
where $E_{\text{min}}$ is the minimum considered flare energy and $X$ is a random number on the interval $[0,1)$. We set the default values $\alpha=-0.829$, $\beta=26.87$ from \citet{gao2022}, but these can be adjusted by the user. Figure \ref{fig:flare_freq} shows our simulation results compared to their power-law values.
